Data Management for LSST Special Programs

### 2024-03-27 sec_sci.tex
JB comment

\textbf{Caveat I. The scope} of Special Processing is at the discretion of
Rubin Data Management, including the timelines for data releases.

\textbf{Caveat II. The definition of possible} comes from the requirement referenced
for the first motivation in the list above (i.e., is not defined by this document).
However, this definition failed to recognize cost-benefit tradeoffs to implementing
and operating Special Processing, and does not account for the costs of operating,
documenting, and maintaining additional processing campaigns and their data products.
Furthermore, the science goals and complexity of Special Programs might evolve
significantly over the 10 year survey.
Even in situations that require no algorithmic or software development,
the Rubin DM team might not have the staffing to handle Special Processing
for all cases that are technically "possible".

\textbf{Caveat III. The definition of necessary} is defined here in this document only.
We emphasize that the term applies only to the \emph{primary} science goals, and does
not cover secondary or "bespoke" science goals for a Special Program.
Users should anticipate that User-Generated Processing will be needed for these cases.

The definitions of possible and necessary are further illustrated with examples in Section~\ref{ssec:proc_special}.

>>>>

The scope of Special Processing is at the discretion of
Rubin Data Management, including the timelines for data releases,
and there are two caveats to add to the above definitions.

\textbf{Caveat I. The definition of possible} comes from the requirement referenced
for the first motivation in the list above (i.e., is not defined by this document).
However, this definition failed to recognize cost-benefit tradeoffs to implementing
and operating Special Processing, and does not account for the costs of operating,
documenting, and maintaining additional processing campaigns and their data products.
Even in situations that require no algorithmic or software development,
the Rubin DM team might not have the staffing to handle Special Processing
for all cases that are technically "possible".
Current ballpark estimates are that the DM effort for Special Processing
should be commeasurate with the 10\% level estimated for survey time,
storage space, and computational resources allocated for Special Programs.

\textbf{Caveat II. The definition of necessary} is defined here in this document only.
We emphasize that the term applies only to the \emph{primary} science goals, and does
not cover secondary or "bespoke" science goals for a Special Program.
Users should anticipate that User-Generated Processing will be needed for these cases.

The definitions of possible and necessary are further illustrated with examples of when
Special Processing vs. User-Generate Processing will be needed, in Sections
\ref{ssec:proc_special} and \ref{ssec:proc_user}, respectively.
